Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Fix non-compliant unicode characters
Add note about building elevation, Biljecki

Depending on the level of data we have access to, we can then choose what level of representation we would like for our application (Todor).

Another crucial concept in city modelling is the Level Of Detail (LOD). LOD is a definition of a series of different 3D representation of the same data, at different detail levels.
The LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
LOD-A models are renderings of the building footprint itself, or building blocks that have been extruded from the footprint to give the building height.
LOD-B models are building blocks with simplifed roof shapes, and LOD-C models include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\textbf{(Biljecki, Ledoux and Stoter, 2016)}
We may also chose what LOD class(es) to use depending on data availablity and application.
With the current means of data aquisition being limited to building footprints, using OSM data we can only produce CityGML 
If we wish to aqquire building assets at a LOD-C level, we would have to complete the data with other sources, or rely on procedural methods to populate.
Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using shape grammar: a method for iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, with the induction of random fluctuations.
For simple presentation in e.g. animation and videogames or even urban planning software, this could very well be enough.
The problem is that these features will rarely match real life.
As long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.

@@

\bibitem{douglas-73}
Douglas, D.H. and Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

@@

\bibitem{stojanovski-19}
Stojanovski, T. (2019). Typo-morphology of transportation -Looking at historical development and multimodal futures of Swedish streets and roads. Conference paper. ISUF 2019 – ХХVI International Seminar on Urban Form 2019, At Nicosia, Cyprus

>>>>

Building elevation. Occasinally buildings in OSM may be tagged, but the norm is that no elevation data is available.
\textbf{(Biljecki, Ledoux and Stoter, 2017)} presented a method for inferring building height exclusively from the building footprint and surrounding footprints.
Surprisingly, their model was shown to be accurace within a meter on average.

Another crucial concept in city modelling is the Level Of Detail (LOD). LOD is a definition of a series of different 3D representation of the same data, at different detail levels.
The LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
LOD-A models are renderings of the building footprint itself, or building blocks that have been extruded from the footprint to give the building height.
LOD-B models are building blocks with simplifed roof shapes, and LOD-C models include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\textbf{(Biljecki et al, 2016)}
We may also chose what LOD class(es) to use depending on data availablity and application.
With the current means of data aquisition being limited to building footprints, using OSM data we can only produce CityGML 
If we wish to aqquire building assets at a LOD-C level, we would have to complete the data with other sources, or rely on procedural methods to populate.
Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using shape grammar: a method for iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, with the induction of random fluctuations.
For simple presentation in e.g. animation and videogames or even urban planning software, this could very well be enough.
The problem is that these features will rarely match real life.
As long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.

@@

\bibitem{biljecki-17}
Biljecki, F., Ledoux, H. and Stoter, J. (2017). Generating 3D city models without elevation data. Computers Environment and Urban Systems. 64. 1-18. 10.1016/j.compenvurbsys.2017.01.001. 
\bibitem{douglas-73}
Douglas, D.H. and Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

@@

\bibitem{stojanovski-19}
Stojanovski, T. (2019). Typo-morphology of transportation -Looking at historical development and multimodal futures of Swedish streets and roads. Conference paper. ISUF 2019 -XXVI International Seminar on Urban Form 2019, At Nicosia, Cyprus
